Computational musicology, ????, Profit

### 2016-07-24 paper.tex
Incorporate plaguerism stuff and computer-as-instrument stuff.

Such judgements are perilous from a musicological point of view, as they are often based on a jury's intuition as to
the similarity between songs and not, for example, on a conditional Kolmogorov complexity analysis of the distance between
the two compositions.

As a response to this situation, I decided to compose a track that would infringe on the copyright of both songs. The following
piece decodes the Champernowne word into music.

@@

Nothing in the the \verb|copyright-infringement-song|'s description is in any way related to `Blurred Lines'.
It is simply a straightforward musical rendering of a well-known mathematical constant derived from the decimal counting
system.

@@

Here we finally come to the profit generation strategy - copyright litigation. As the \verb|copyright-infringement-song| is
a universal piece of music, any work published subsequent to it infringes on its copyright.~\footnote{I am not a lawyer. Do not rely on my legal advice.} In order to convert our computational musicology understanding into profit, we simply have to
sue the composers of every marginally successful musical work from now until they fix the law. Previous works have used
complexity analyses to detect copyright infringement\cite{Intrinsic Plaguerism Detection}. Here we take that one step further
and use complexity theory to cause copyright infringement.

>>>>

Such judgements are perilous from a musicological point of view, as they are often based on a jury's intuition as to
the similarity between songs and not, for example, on a conditional Kolmogorov complexity analysis of the distance between
the two compositions, for example in the manner Seaward and Matwin suggest for textual plaguerism\cite{Intrinsic Plaguerism Detection}.

As a response to this situation, I decided to compose a track that would infringe on the copyright of both songs. In doing so, I
am participating in a long tradition of computer-aided composition, described for example in M. V. Mathews' 1963 paper
``The Digital Computer as a Musical Instrument"\cite{The Digital Computer as a Musical Instrument}.

The following piece decodes the Champernowne word into music.

@@

Nothing in the the \verb|copyright-infringement-song|'s description is in any way related to `Blurred Lines'.
It is simply a straightforward musical rendering of a well-known mathematical constant derived from the decimal counting
system. This is a degenerate case of M. V. Mathews' vision that music coding would allow a composer to
``write directly in parameters that are much more
closely related to his musical objectives, letting the machine generate the individual
notes"\cite{The Digital Computer as a Musical Instrument}.

@@

Here we finally come to the profit generation strategy - copyright litigation. As the \verb|copyright-infringement-song| is
a universal piece of music, any work published subsequent to it infringes on its copyright.~\footnote{I am not a lawyer. Do not rely on my legal advice.} In order to convert our computational musicology understanding into profit, we simply have to
sue the composers of every marginally successful musical work from now until they fix the law. Previous works such as Seaward
and Matwin's paper have used complexity analyses to detect copyright infringement\cite{Intrinsic Plaguerism Detection}.
Here we have taken that one step further and use complexity theory to cause copyright infringement.
